Make any stupid plot you want

### 2021-02-15 draft/sections/next.tex
trying to sort out diff from mackinlay

Other things that may or may not play a big role would be working out the details of the S->K interaction for dashboards. By this I particularly mean when S is a composite object spanning all the figures shown in the dashboard and a component of K may have different compoents of S mapping into it slicing it in different ways.
\subsection{What are the lessons learned?}

>>>>

Other things that may or may not play a big role would be working out the details of the S->K interaction for dashboards. By this I particularly mean when S is a composite object spanning all the figures shown in the dashboard and a component of K may have different components of S mapping into it slicing it in different ways.
\subsection{What are the lessons learned?}
